Quantifying the ease of viral escape from broad and narrow antibodies to influenza hemagglutinin

### 2017-10-18 paper/manuscript.tex
Some minor additions to methods

\subsection*{Neutralization assays}
\comment{add this}

\subsection*{Mutant virus selections with antibody and deep sequencing}
Library selections, deep sequencing, and computation of mutation differential selection were performed as previously described~\cite{doud2017complete}.

>>>>

\subsection*{Neutralization assays}
We performed neutralization assays as previously described in ~\citep{}.
\comment{going to add more here}

\subsection*{Mutant virus selections with antibody and deep sequencing}
Library selections, deep sequencing, and computation of mutation differential selection were performed as previously described in ~\cite{doud2017complete}.

To estimate the fraction of the overall library surviving selection, we used a standard curve by making 10-fold serial dilutions of the virus libraries
